---
title: "Interactions"
author: "Lillian Dillard"
date: '2022-11-21'
output: html_document
---

```{r setup, include=FALSE}
library(dplyr)
library(plyr)
library(readr)
library(data.table)
library(stringr)
library(ggplot2)
library(tidyr)
library(corrplot)
library(gdata)
library(readxl)
library(vegan)
library(pheatmap)
library(viridis)
library(gg.gap) 


colors2 <- c("#9DAD9D","#224B5D")
```

```{r setup, include=FALSE}
competition_flux_change <- read_delim("~/vaginal_microbiome/interactions/competition_flux_change_all.csv", 
    "\t", escape_double = FALSE, trim_ws = TRUE) %>% na.omit() %>% select(-X1)
competition_metabolites_all <- read_delim("~/vaginal_microbiome/interactions/competition_metabolites_all.csv", 
    "\t", escape_double = FALSE, trim_ws = TRUE) %>% na.omit() %>% select(-c(X1,iteration, times_contested))

mutual_metabolites_all <- read_delim("~/vaginal_microbiome/interactions/mutual_metabolites_all.csv", 
    "\t", escape_double = FALSE, trim_ws = TRUE) %>% na.omit() %>% filter(direction != "base_medium") %>% select(-c(X1, iteration))
                                                                                                                                  
mutual_flux_change <- read_delim("~/vaginal_microbiome/interactions/mutual_flux_change_all.csv", 
    "\t", escape_double = FALSE, trim_ws = TRUE) %>% na.omit() %>% select(-X1)

Strain_Reclassifications <- read_excel("~/Documents/interactions_paper/Strain_Reclassifications.xlsx")

BVBRC_genome <- read_excel("~/Documents/interactions_paper/BVBRC_genome.xls", 
    col_types = c("text", "text", "skip", 
        "skip", "text", "skip", "skip", "text", 
        "skip", "skip", "skip", "skip", "skip", 
        "skip", "skip", "skip", 
        "skip", "skip", "skip", 
        "skip", "skip", "skip", 
        "skip", "skip", "skip", 
        "skip", "skip", "skip", 
        "skip", "skip", "skip", 
        "skip", "skip", "skip", 
        "skip", "skip", "skip", 
        "skip", "skip", "skip", 
        "skip", "skip", "skip", 
        "skip", "skip", "skip", 
        "skip", "skip", "skip", "skip", 
        "skip", "skip"))

BVBRC_genome$`Assembly Accession` <- gsub("GCF","GCA",BVBRC_genome$`Assembly Accession`)


metadata <- full_join(BVBRC_genome, Strain_Reclassifications)
remove_genomes <- c("2702.504", "2702.496", "2702.490", "2702.348", "2702.299", "293424.12",
                       "293424.14","2702.477","293424.19","2702.494","293424.16",
                    "2702.4769999999999","2702.4899999999998", "2702.4940000000001",
                    "2702.4960000000001", "2702.5039999999999", "293424.14000000001",
                    "293424.15999999997", "626522.30000000005", "2702.9299999999998",
                    "2702.9400000000001", "2702.9499999999998", "2702.96")
metadata <- metadata[ ! metadata$`Genome ID` %in% remove_genomes,]

metadata$Reclassification <- replace_na(metadata$Reclassification, "No Ascension")

metadata$Reclassification <- as.factor(metadata$Reclassification)
```

# Mutualism
```{r}
#Remove erroneous 13 genomes now
remove_genomes <- c("2702.504", "2702.496", "2702.490", "2702.348", "2702.299", "293424.12",
                       "293424.14","2702.477","293424.19","2702.494","293424.16", "293424.21",
                    "626522.3", "2702.93", "2702.94", "2702.95", "2702.96")

competition_metabolites_all$genre1 <- gsub(".*/","",competition_metabolites_all$genre1)
competition_metabolites_all$genre1 <- gsub(".sbml*","",competition_metabolites_all$genre1)
competition_metabolites_all$genre2 <- gsub(".*/","",competition_metabolites_all$genre2)
competition_metabolites_all$genre2 <- gsub(".sbml*","",competition_metabolites_all$genre2)

mutual_metabolites_all$genre1 <- gsub(".*/","",mutual_metabolites_all$genre1)
mutual_metabolites_all$genre1 <- gsub(".sbml*","",mutual_metabolites_all$genre1)
mutual_metabolites_all$genre2 <- gsub(".*/","",mutual_metabolites_all$genre2)
mutual_metabolites_all$genre2 <- gsub(".sbml*","",mutual_metabolites_all$genre2)

competition_metabolites_all <- competition_metabolites_all[ ! competition_metabolites_all$genre1 %in% remove_genomes & ! competition_metabolites_all$genre2 %in% remove_genomes, ]
mutual_metabolites_all <- mutual_metabolites_all[ ! mutual_metabolites_all$genre1 %in% remove_genomes & ! mutual_metabolites_all$genre2 %in% remove_genomes, ]

competition_flux_change$GENRE1_Flux_Dec <- (as.numeric(competition_flux_change$GENRE1_preFlux) - as.numeric(competition_flux_change$GENRE1_compFlux))

competition_flux_change$GENRE2_Flux_Dec <- (as.numeric(competition_flux_change$GENRE2_preFlux) - as.numeric(competition_flux_change$GENRE2_compFlux)) 

competition_flux_change <- competition_flux_change %>% select(-c(2:5))

competition_flux_change[c('GENRE1', 'GENRE2')] <- str_split_fixed(competition_flux_change$Comparison, ',', 2)
competition_flux_change$Comparison <- NULL
competition_flux_change$GENRE1 <- gsub(".*/","",competition_flux_change$GENRE1)
competition_flux_change$GENRE1 <- gsub(".sb.*","",competition_flux_change$GENRE1)
competition_flux_change$GENRE2 <- gsub(".*/","",competition_flux_change$GENRE2)
competition_flux_change$GENRE2 <- gsub(".sb.*","",competition_flux_change$GENRE2)
competition_flux_change$GENRE2 <- gsub(".xml.*","",competition_flux_change$GENRE2)
competition_flux_change$GENRE1 <- gsub(".xml.*","",competition_flux_change$GENRE1)

competition_flux_change <- competition_flux_change[ ! competition_flux_change$GENRE1 %in% remove_genomes & ! competition_flux_change$GENRE2 %in% remove_genomes, ]

mutual_flux_change[c('GENRE1', 'GENRE2')] <- str_split_fixed(mutual_flux_change$Comparison, ',', 2)
mutual_flux_change$Comparison <- NULL
mutual_flux_change$GENRE1 <- gsub(".*/","",mutual_flux_change$GENRE1)
mutual_flux_change$GENRE1 <- gsub(".sb.*","",mutual_flux_change$GENRE1)
mutual_flux_change$GENRE2 <- gsub(".*/","",mutual_flux_change$GENRE2)
mutual_flux_change$GENRE2 <- gsub(".sb.*","",mutual_flux_change$GENRE2)
mutual_flux_change$GENRE2 <- gsub(".xml.*","",mutual_flux_change$GENRE2)
mutual_flux_change$GENRE1 <- gsub(".xml.*","",mutual_flux_change$GENRE1)

mutual_flux_change <- mutual_flux_change[ ! mutual_flux_change$GENRE1 %in% remove_genomes & ! mutual_flux_change$GENRE2 %in% remove_genomes, ]

```

## tSNE
```{r}
alltheinfo <- full_join(mutual_flux_change, competition_flux_change)
GENRE1_mutualism <- data.frame(alltheinfo$GENRE1, alltheinfo$GENRE2,alltheinfo$GENRE1_Flux_Inc)
GENRE2_mutualism <- data.frame(alltheinfo$GENRE2, alltheinfo$GENRE1,alltheinfo$GENRE2_Flux_Inc)

colnames(GENRE1_mutualism) <- c("GENRE1", "GENRE2","GENRE1_Flux_Inc")
colnames(GENRE2_mutualism) <- c("GENRE1", "GENRE2","GENRE1_Flux_Inc")
GENRE_mutualism <- rbind(GENRE1_mutualism, GENRE2_mutualism)

GENRE_mutualism <- pivot_wider(GENRE_mutualism, names_from = "GENRE2", values_from ="GENRE1_Flux_Inc")

metadata$`Genome ID`<- as.character(as.numeric(metadata$`Genome ID`))
colnames(metadata)[1]<- "GENRE1"

GENRE_mutualism <- left_join(GENRE_mutualism, metadata)
GENRE <- GENRE_mutualism$GENRE1
GENRE_mutualism <- subset(GENRE_mutualism, select = -c(`Genome Name`,`Strain`,`Assembly Accession`, GENRE1))

GENRE_mutualism$Reclassification <- gsub("Gardnerella-1","Gardnerella-1,2,3,4",GENRE_mutualism$Reclassification)
GENRE_mutualism$Reclassification <- gsub("Gardnerella-2","Gardnerella-1,2,3,4",GENRE_mutualism$Reclassification)
GENRE_mutualism$Reclassification <- gsub("Gardnerella-3","Gardnerella-1,2,3,4",GENRE_mutualism$Reclassification)
GENRE_mutualism$Reclassification <- gsub("Gardnerella-4","Gardnerella-1,2,3,4",GENRE_mutualism$Reclassification)

GENRE_mutualism$Reclassification <- gsub("Gardnerella-5","Gardnerella-5,6,7,8,9",GENRE_mutualism$Reclassification)
GENRE_mutualism$Reclassification <- gsub("Gardnerella-6","Gardnerella-5,6,7,8,9",GENRE_mutualism$Reclassification)
GENRE_mutualism$Reclassification <- gsub("Gardnerella-7","Gardnerella-5,6,7,8,9",GENRE_mutualism$Reclassification)
GENRE_mutualism$Reclassification <- gsub("Gardnerella-8","Gardnerella-5,6,7,8,9",GENRE_mutualism$Reclassification)
GENRE_mutualism$Reclassification <- gsub("Gardnerella-9","Gardnerella-5,6,7,8,9",GENRE_mutualism$Reclassification)

GENRE_mutualism$Reclassification <- gsub("Gardnerella piotii A","Gardnerella piotti",GENRE_mutualism$Reclassification)
GENRE_mutualism$Reclassification <- gsub("Gardnerella piotii B","Gardnerella piotti",GENRE_mutualism$Reclassification)

GENRE_mutualism$Reclassification <- gsub("Gardnerella vaginalis A","Gardnerella vaginalis",GENRE_mutualism$Reclassification)
GENRE_mutualism$Reclassification <- gsub("Gardnerella vaginalis B","Gardnerella vaginalis",GENRE_mutualism$Reclassification)

GENRE_mutualism$Reclassification <- gsub("No Ascension","Unknown",GENRE_mutualism$Reclassification)
GENRE_mutualism[is.na(GENRE_mutualism)] <- "Unknown"
```

```{r model3_NMDS, echo=TRUE}
response <- as.factor(GENRE_mutualism$Reclassification)
input_mutualism <- subset(GENRE_mutualism, select=-c(Reclassification))
input_mutualism <- mutate_all(input_mutualism, function(x) as.numeric(as.character(x)))
input_mutualism[is.na(input_mutualism)] <- 0

set.seed(10)

library(Rtsne)
tsne_out <- Rtsne(input_mutualism, perplexity =14, max_iter = 50000)
tsne_plot <- data.frame(x = tsne_out$Y[,1],
                        y = tsne_out$Y[,2])
tsne_plot$model <- response
```

```{r}
colors3 <- c("#f0a04b","#613daa","#b1615c","#d88782","#e3aba7","#dec5da","#edd7d9","#ffe6b7","#c3c20e","#72bcd5","#c1d1aa","#97c684","#466c4b","#D4D4D4")

colors4 <- c("#f0a04b","#613daa","#e3aba7","#c3c20e","#72bcd5","#97c684","#D4D4D4")
```

```{r}
pdf(file='~/Documents/interactions_paper/mutualism_tSNE_complex.pdf', width=7, height=7)

ggplot(tsne_plot) + 
  geom_point(aes(x=x,y=y,colour=model),size=2) +
  theme_classic() + 
  theme(axis.title.x=element_blank(),
        axis.title.y = element_blank()) +
  scale_color_manual(values = colors3, name = "Bacterial Classification") +
  ggtitle("Mutualism Flux tSNE")+
  theme(plot.title = element_text(hjust = 0.5, size = 15, face="bold"),
        legend.title = element_text(face = "bold"), legend.text = element_text(face = "italic", size = 10))

dev.off()
```

## tSNE Simplified
```{r}
response <- gsub("Prevotella amnii","Prevotella",response)
response <- gsub("Prevotella bivia","Prevotella",response)
response <- gsub("Prevotella tannerae","Prevotella",response)
response <- gsub("Prevotella buccalis","Prevotella",response)
response <- gsub("Gardnerella vaginalis", "Gardnerella",response)
response <- gsub("Gardnerella leopoldii", "Gardnerella",response)
response <- gsub("Gardnerella swidsinskii", "Gardnerella",response)
response <- gsub("Gardnerella piotti", "Gardnerella",response)
response <- gsub("Gardnerella-1,2,3,4", "Gardnerella",response)
response <- gsub("Gardnerella-5,6,7,8,9", "Gardnerella",response)

tsne_plot$model <- response
```

```{r}
pdf(file='~/Documents/interactions_paper/mutualism_tSNE_simple.pdf', width=7, height=7)

ggplot(tsne_plot) + 
  geom_point(aes(x=x,y=y,colour=model),size=2) +
  theme_classic() + 
  theme(axis.title.x=element_blank(),
        axis.title.y = element_blank()) +
  scale_color_manual(values = colors4, name = "Bacterial Classification") +
  ggtitle("Mutualism Flux tSNE")+
  theme(plot.title = element_text(hjust = 0.5, size = 15, face="bold"),
        legend.title = element_text(face = "bold"), legend.text = element_text(face = "italic", size = 10))

dev.off()
```


```{r}
annotation_row <- data.frame(
  Bacterial_Species = as.factor(response)
)

annoCol = list(Bacterial_Species = c(`Aerococcus christensenii` = "#f0a04b",
                                     `Fannyhessea vaginae`="#613daa",
                                     `Gardnerella`= "#e3aba7",
                                     `Lactobacillus iners` = "#72bcd5",
                                     `Hoylesella timonensis` = "#c3c20e",
                                     `Prevotella` = "#97c684",
                                     `Unknown`="#D4D4D4"))


rownames(annotation_row) <- GENRE
rownames(input_mutualism) <- GENRE
```

```{r}
library(RColorBrewer)
pdf(file='~/Documents/interactions_paper/mutualism_heatmap.pdf', width=10, height=7)
pheatmap(input_mutualism,  border_color = NA,
         show_rownames = FALSE, 
         annotation_names_col = FALSE,
         clustering_method = "ward.D", color = colorRampPalette(brewer.pal(n = 7, name =
  "Blues"))(10), cutree_rows = 5, cutree_cols = 3,
         cellwidth = 2, cellheight = 2,
         width = 10, height = 12, annotation_row = annotation_row,
         annotation_col = annotation_row, annotation_colors = annoCol,
         show_colnames = FALSE, annotation_names_row = FALSE)
dev.off()
```

# Competition
## tSNE
```{r}
GENRE1_competition <- data.frame(alltheinfo$GENRE1, alltheinfo$GENRE2,alltheinfo$GENRE1_Flux_Dec)
GENRE2_competition <- data.frame(alltheinfo$GENRE2, alltheinfo$GENRE1,alltheinfo$GENRE2_Flux_Dec)

colnames(GENRE1_competition) <- c("GENRE1", "GENRE2","GENRE1_Flux_Dec")
colnames(GENRE2_competition) <- c("GENRE1", "GENRE2","GENRE1_Flux_Dec")
GENRE_competition <- rbind(GENRE1_competition, GENRE2_competition)

GENRE_competition <- pivot_wider(GENRE_competition, names_from = "GENRE2", values_from ="GENRE1_Flux_Dec")

GENRE_competition <- left_join(GENRE_competition, metadata)
competition_matrix <- left_join(GENRE_competition, metadata)
GENRE <- GENRE_competition$GENRE1
GENRE_competition <- subset(GENRE_competition, select = -c(`Genome Name`,`Strain`,`Assembly Accession`, GENRE1))

GENRE_competition$Reclassification <- gsub("Gardnerella-1","Gardnerella-1,2,3,4",GENRE_competition$Reclassification)
GENRE_competition$Reclassification <- gsub("Gardnerella-2","Gardnerella-1,2,3,4",GENRE_competition$Reclassification)
GENRE_competition$Reclassification <- gsub("Gardnerella-3","Gardnerella-1,2,3,4",GENRE_competition$Reclassification)
GENRE_competition$Reclassification <- gsub("Gardnerella-4","Gardnerella-1,2,3,4",GENRE_competition$Reclassification)

GENRE_competition$Reclassification <- gsub("Gardnerella-5","Gardnerella-5,6,7,8,9",GENRE_competition$Reclassification)
GENRE_competition$Reclassification <- gsub("Gardnerella-6","Gardnerella-5,6,7,8,9",GENRE_competition$Reclassification)
GENRE_competition$Reclassification <- gsub("Gardnerella-7","Gardnerella-5,6,7,8,9",GENRE_competition$Reclassification)
GENRE_competition$Reclassification <- gsub("Gardnerella-8","Gardnerella-5,6,7,8,9",GENRE_competition$Reclassification)
GENRE_competition$Reclassification <- gsub("Gardnerella-9","Gardnerella-5,6,7,8,9",GENRE_competition$Reclassification)

GENRE_competition$Reclassification <- gsub("Gardnerella piotii A","Gardnerella piotti",GENRE_competition$Reclassification)
GENRE_competition$Reclassification <- gsub("Gardnerella piotii B","Gardnerella piotti",GENRE_competition$Reclassification)

GENRE_competition$Reclassification <- gsub("Gardnerella vaginalis A","Gardnerella vaginalis",GENRE_competition$Reclassification)
GENRE_competition$Reclassification <- gsub("Gardnerella vaginalis B","Gardnerella vaginalis",GENRE_competition$Reclassification)

GENRE_competition$Reclassification <- gsub("No Ascension","Unknown",GENRE_competition$Reclassification)
```

```{r model3_NMDS, echo=TRUE}
response <- as.factor(GENRE_competition$Reclassification)
input_competition <- subset(GENRE_competition, select=-c(Reclassification))
input_competition <- mutate_all(input_competition, function(x) as.numeric(as.character(x)))
input_competition[is.na(input_competition)] <- 0

set.seed(10)
tsne_out <- Rtsne(input_competition, check_duplicates = FALSE, perplexity = 14, max_iter = 50000)
tsne_plot <- data.frame(x = tsne_out$Y[,1],
                        y = tsne_out$Y[,2])
tsne_plot$model <- response
```

```{r}
pdf(file='~/Documents/interactions_paper/competition_tSNE_complex.pdf', width=7, height=7)

ggplot(tsne_plot) + 
  geom_point(aes(x=x,y=y,colour=model),size=2) +
  theme_classic() + 
  theme(axis.title.x=element_blank(),
        axis.title.y = element_blank()) +
  scale_color_manual(values = colors3, name = "Bacterial Classification") +
  ggtitle("Competition Flux tSNE")+
  theme(plot.title = element_text(hjust = 0.5, size = 15, face="bold"),
        legend.title = element_text(face = "bold"), legend.text = element_text(face = "italic", size = 10))

dev.off()
```

## tSNE Simplified
```{r}
response <- gsub("Prevotella amnii","Prevotella",response)
response <- gsub("Prevotella bivia","Prevotella",response)
response <- gsub("Prevotella tannerae","Prevotella",response)
response <- gsub("Prevotella buccalis","Prevotella",response)
response <- gsub("Gardnerella vaginalis", "Gardnerella",response)
response <- gsub("Gardnerella leopoldii", "Gardnerella",response)
response <- gsub("Gardnerella swidsinskii", "Gardnerella",response)
response <- gsub("Gardnerella piotti", "Gardnerella",response)
response <- gsub("Gardnerella-1,2,3,4", "Gardnerella",response)
response <- gsub("Gardnerella-5,6,7,8,9", "Gardnerella",response)

tsne_plot$model <- response
```

```{r}
pdf(file='~/Documents/interactions_paper/competition_tSNE_simple.pdf', width=7, height=7)

ggplot(tsne_plot) + 
  geom_point(aes(x=x,y=y,colour=model),size=2) +
  theme_classic() + 
  theme(axis.title.x=element_blank(),
        axis.title.y = element_blank()) +
  scale_color_manual(values = colors4, name = "Bacterial Classification") +
  ggtitle("Competition Flux tSNE")+
  theme(plot.title = element_text(hjust = 0.5, size = 15, face="bold"),
        legend.title = element_text(face = "bold"), legend.text = element_text(face = "italic", size = 10))


dev.off()
```

```{r}
annotation_row <- data.frame(
  Bacterial_Species = as.factor(response)
)

rownames(annotation_row) <- GENRE
rownames(input_competition) <- GENRE
```

```{r}
library(RColorBrewer)
pdf(file='~/Documents/interactions_paper/competition_heatmap.pdf', width=10, height=7)

pheatmap(input_competition,  border_color = NA,
         show_rownames = FALSE, show_colnames = FALSE, cutree_rows = 4, cutree_cols = 3,
         clustering_method = "ward.D", annotation_colors = annoCol,
         cellwidth = 2, cellheight = 2,
         color = colorRampPalette(brewer.pal(n = 7, name = "Blues"))(10),
         width = 10, height = 12, annotation_row = annotation_row,
         annotation_col = annotation_row, annotation_names_row = FALSE, annotation_names_col = FALSE)
dev.off()
```

# Net Interactions Flux Values
```{r}
GENRE1_competition <- data.frame(alltheinfo$GENRE1, alltheinfo$GENRE2,alltheinfo$GENRE1_Flux_Dec)
GENRE2_competition <- data.frame(alltheinfo$GENRE2, alltheinfo$GENRE1,alltheinfo$GENRE2_Flux_Dec)

colnames(GENRE1_competition) <- c("GENRE1", "GENRE2","GENRE1_Flux_Dec")
colnames(GENRE2_competition) <- c("GENRE1", "GENRE2","GENRE1_Flux_Dec")
GENRE_competition <- rbind(GENRE1_competition, GENRE2_competition)

GENRE1_mutualism <- data.frame(alltheinfo$GENRE1, alltheinfo$GENRE2,alltheinfo$GENRE1_Flux_Inc)
GENRE2_mutualism <- data.frame(alltheinfo$GENRE2, alltheinfo$GENRE1,alltheinfo$GENRE2_Flux_Inc)

colnames(GENRE1_mutualism) <- c("GENRE1", "GENRE2","GENRE1_Flux_Inc")
colnames(GENRE2_mutualism) <- c("GENRE1", "GENRE2","GENRE1_Flux_Inc")
GENRE_mutualism <- rbind(GENRE1_mutualism, GENRE2_mutualism)

GENRE_net <- left_join(GENRE_competition, GENRE_mutualism)
GENRE_net$netflux <- as.numeric(GENRE_net$GENRE1_Flux_Inc) - as.numeric(GENRE_net$GENRE1_Flux_Dec)
GENRE_net$GENRE1_Flux_Inc <- NULL
GENRE_net$GENRE1_Flux_Dec <- NULL

GENRE_net <- pivot_wider(GENRE_net, names_from = "GENRE2", values_from ="netflux")

GENRE_net <- left_join(GENRE_net, metadata)
GENRE <- GENRE_net$GENRE1
GENRE_net <- subset(GENRE_net, select = -c(`Genome Name`,`Strain`,`Assembly Accession`, GENRE1))

GENRE_net$Reclassification <- gsub("Gardnerella-1","Gardnerella-1,2,3,4",GENRE_net$Reclassification)
GENRE_net$Reclassification <- gsub("Gardnerella-2","Gardnerella-1,2,3,4",GENRE_net$Reclassification)
GENRE_net$Reclassification <- gsub("Gardnerella-3","Gardnerella-1,2,3,4",GENRE_net$Reclassification)
GENRE_net$Reclassification <- gsub("Gardnerella-4","Gardnerella-1,2,3,4",GENRE_net$Reclassification)

GENRE_net$Reclassification <- gsub("Gardnerella-5","Gardnerella-5,6,7,8,9",GENRE_net$Reclassification)
GENRE_net$Reclassification <- gsub("Gardnerella-6","Gardnerella-5,6,7,8,9",GENRE_net$Reclassification)
GENRE_net$Reclassification <- gsub("Gardnerella-7","Gardnerella-5,6,7,8,9",GENRE_net$Reclassification)
GENRE_net$Reclassification <- gsub("Gardnerella-8","Gardnerella-5,6,7,8,9",GENRE_net$Reclassification)
GENRE_net$Reclassification <- gsub("Gardnerella-9","Gardnerella-5,6,7,8,9",GENRE_net$Reclassification)

GENRE_net$Reclassification <- gsub("Gardnerella piotii A","Gardnerella piotti",GENRE_net$Reclassification)
GENRE_net$Reclassification <- gsub("Gardnerella piotii B","Gardnerella piotti",GENRE_net$Reclassification)

GENRE_net$Reclassification <- gsub("Gardnerella vaginalis A","Gardnerella vaginalis",GENRE_net$Reclassification)
GENRE_net$Reclassification <- gsub("Gardnerella vaginalis B","Gardnerella vaginalis",GENRE_net$Reclassification)


GENRE_net$Reclassification <- gsub("No Ascension","Unknown",GENRE_net$Reclassification)
```

## tSNE
```{r model3_NMDS, echo=TRUE}
response <- as.factor(GENRE_net$Reclassification)
input_net <- subset(GENRE_net, select=-c(Reclassification))
input_net <- mutate_all(input_net, function(x) as.numeric(as.character(x)))
input_net[is.na(input_net)] <- 0

set.seed(10)
tsne_out <- Rtsne(input_net, check_duplicates = FALSE, perplexity = 14, max_iter = 50000)
tsne_plot <- data.frame(x = tsne_out$Y[,1],
                        y = tsne_out$Y[,2])
tsne_plot$model <- response
```

```{r}
pdf(file='~/Documents/interactions_paper/netflux_tSNE_complex.pdf', width=7, height=7)

ggplot(tsne_plot) + 
  geom_point(aes(x=x,y=y,colour=model),size=2) +
  theme_classic() + 
  theme(axis.title.x=element_blank(),
        axis.title.y = element_blank()) +
  scale_color_manual(values = colors3, name = "Bacterial Species") +
  ggtitle("Net Flux tSNE")+
  theme(plot.title = element_text(hjust = 0.5, size = 15, face="bold"),
        legend.title = element_text(face = "bold"), legend.text = element_text(face = "italic", size = 10))


dev.off()
```

## tSNE Simplified
```{r}
response <- gsub("Prevotella amnii","Prevotella",response)
response <- gsub("Prevotella bivia","Prevotella",response)
response <- gsub("Prevotella tannerae","Prevotella",response)
response <- gsub("Prevotella buccalis","Prevotella",response)
response <- gsub("Gardnerella vaginalis", "Gardnerella",response)
response <- gsub("Gardnerella leopoldii", "Gardnerella",response)
response <- gsub("Gardnerella swidsinskii", "Gardnerella",response)
response <- gsub("Gardnerella piotti", "Gardnerella",response)
response <- gsub("Gardnerella-1,2,3,4", "Gardnerella",response)
response <- gsub("Gardnerella-5,6,7,8,9", "Gardnerella",response)

tsne_plot$model <- response
```

```{r}
pdf(file='~/Documents/interactions_paper/netflux_tSNE_simple.pdf', width=7, height=7)

ggplot(tsne_plot) + 
  geom_point(aes(x=x,y=y,colour=model),size=2) +
  theme_classic() + 
  theme(axis.title.x=element_blank(),
        axis.title.y = element_blank()) +
  scale_color_manual(values = colors4, name = "Bacterial Classification") +
  ggtitle("Net Flux tSNE")+
  theme(plot.title = element_text(hjust = 0.5, size = 15, face="bold"),
        legend.title = element_text(face = "bold"), legend.text = element_text(face = "italic", size = 10))


dev.off()
```

## Heatmap
```{r}
annotation_row <- data.frame(
  Bacterial_Species = as.factor(response)
)

rownames(annotation_row) <- GENRE
rownames(input_net) <- GENRE
```

```{r}
pdf(file='~/Documents/interactions_paper/net_heatmap.pdf', width=10, height=7)

pheatmap(input_net,  border_color = NA,
         show_rownames = FALSE, show_colnames = FALSE, 
         clustering_method = "ward.D", annotation_colors = annoCol,
         cellwidth = 2, cellheight = 2, 
         width = 10, height = 12, cutree_rows = 5, cutree_cols = 3,
         annotation_row = annotation_row,
         annotation_col = annotation_row,
         annotation_names_col = FALSE, annotation_names_row = FALSE)
dev.off()
```

#Competition vs Mutualism 
## Single Points
```{r}
colnames(GENRE2_competition) <- c("GENRE2", "GENRE1", "GENRE2_Flux_Dec")
colnames(GENRE2_mutualism) <- c("GENRE2", "GENRE1", "GENRE2_Flux_Inc")

GENRE2_compvsmut <- full_join(GENRE2_competition, GENRE2_mutualism)
GENRE2_compvsmut$GENRE1 <- NULL

GENRE1_compvsmut <- full_join(GENRE1_competition, GENRE1_mutualism)
GENRE1_compvsmut$GENRE2 <- NULL

colnames(GENRE2_compvsmut) <- colnames(GENRE1_compvsmut)
compvsmut <- rbind(GENRE1_compvsmut, GENRE2_compvsmut)

colnames(metadata)[1] <- "GENRE1"
compvsmut <- left_join(compvsmut, metadata)
compvsmut <- subset(compvsmut, select = -c(`Genome Name`,`Strain`,`Assembly Accession`))

compvsmut$GENRE1 <- as.factor(as.character(compvsmut$GENRE1))

comp_averages <- with(compvsmut, tapply(GENRE1_Flux_Dec, GENRE1, mean)) %>% as.data.frame()
colnames(comp_averages)[1] <- "Competition"
comp_averages$GENRE1 <- rownames(comp_averages)

mut_averages <- with(compvsmut, tapply(as.numeric(GENRE1_Flux_Inc), GENRE1, mean)) %>% as.data.frame()
colnames(mut_averages)[1] <- "Mutualism"
mut_averages$GENRE1 <- rownames(mut_averages)

compvsmut_averages <- full_join(comp_averages,mut_averages)
compvsmut_averages <- left_join(compvsmut_averages, metadata)
compvsmut_averages <- subset(compvsmut_averages, select = -c(`Genome Name`,`Strain`,`Assembly Accession`, `GENRE1`))

compvsmut_averages$Reclassification <- gsub("Gardnerella-1","Gardnerella",compvsmut_averages$Reclassification)
compvsmut_averages$Reclassification <- gsub("Gardnerella-2","Gardnerella",compvsmut_averages$Reclassification)
compvsmut_averages$Reclassification <- gsub("Gardnerella-3","Gardnerella",compvsmut_averages$Reclassification)
compvsmut_averages$Reclassification <- gsub("Gardnerella-4","Gardnerella",compvsmut_averages$Reclassification)

compvsmut_averages$Reclassification <- gsub("Gardnerella-5","Gardnerella",compvsmut_averages$Reclassification)
compvsmut_averages$Reclassification <- gsub("Gardnerella-6","Gardnerella",compvsmut_averages$Reclassification)
compvsmut_averages$Reclassification <- gsub("Gardnerella-7","Gardnerella",compvsmut_averages$Reclassification)
compvsmut_averages$Reclassification <- gsub("Gardnerella-8","Gardnerella",compvsmut_averages$Reclassification)
compvsmut_averages$Reclassification <- gsub("Gardnerella-9","Gardnerella",compvsmut_averages$Reclassification)

compvsmut_averages$Reclassification <- gsub("Gardnerella piotii A","Gardnerella",compvsmut_averages$Reclassification)
compvsmut_averages$Reclassification <- gsub("Gardnerella piotii B","Gardnerella",compvsmut_averages$Reclassification)

compvsmut_averages$Reclassification <- gsub("Gardnerella vaginalis A","Gardnerella",compvsmut_averages$Reclassification)
compvsmut_averages$Reclassification <- gsub("Gardnerella vaginalis B","Gardnerella",compvsmut_averages$Reclassification)

compvsmut_averages$Reclassification <- gsub("No Ascension","Unknown",compvsmut_averages$Reclassification)
compvsmut_averages[is.na(compvsmut_averages)] <- "Unknown"

compvsmut_averages$Reclassification <- gsub("Prevotella amnii","Prevotella",compvsmut_averages$Reclassification)
compvsmut_averages$Reclassification <- gsub("Prevotella bivia","Prevotella",compvsmut_averages$Reclassification)
compvsmut_averages$Reclassification <- gsub("Prevotella tannerae","Prevotella",compvsmut_averages$Reclassification)
compvsmut_averages$Reclassification <- gsub("Prevotella buccalis","Prevotella",compvsmut_averages$Reclassification)

compvsmut_averages$Reclassification <- gsub("Gardnerella leopoldii", "Gardnerella",compvsmut_averages$Reclassification)
compvsmut_averages$Reclassification <- gsub("Gardnerella swidsinskii", "Gardnerella",compvsmut_averages$Reclassification)

compvsmut_averages$Reclassification <- as.factor(compvsmut_averages$Reclassification)
```

```{r}
pdf(file='~/Documents/interactions_paper/compevsmut_average.pdf', width=10, height=10)

ggplot(compvsmut_averages) + 
  geom_point(aes(x=Mutualism,y=Competition,colour=Reclassification),size=4, alpha = 0.8) +
  theme_classic()  +
  scale_color_manual(values = colors4, name = "Bacterial Species") +
  ylab("Competition Cost\n") + xlab("Mutualism Benefit\n") +
  theme(axis.title = element_text(hjust = 0.5, size = 20,face="bold"),
        axis.text = element_text(size = 15),
        legend.title = element_text(face="bold")) +
  scale_x_continuous(breaks=c(0,250,500), labels=c("0" = "Low Benefit", "250" = "250", "500" = "High Benefit"))+
  scale_y_continuous(breaks=c(0,200,375,400), labels=c("0" = "Low Cost", "200" = "200", "375" ="375", "400" = "High Cost"))

dev.off()
```

## Competed for Metabolites

```{r cars}
competed_metabolites <- count(competition_metabolites_all$metabolite)
competed_metabolites$percent <- (competed_metabolites$freq/19427) * 100
competed_metabolites <- arrange(competed_metabolites,desc(freq)) %>% filter(percent >= 30) %>% select(-freq) 
competed_metabolites <- competed_metabolites %>% dplyr::rename("Metabolite" = "x", "Competition" = "percent")
```

## Shared Metabolites

You can also embed plots, for example:

```{r pressure, echo=FALSE}
mutual_metabolites <- count(mutual_metabolites_all$metabolite)
mutual_metabolites$percent <- (mutual_metabolites$freq/19427) * 100
mutual_metabolites <- arrange(mutual_metabolites,desc(freq)) %>% filter(percent >= 30)  %>% select(-freq) 
mutual_metabolites <- mutual_metabolites %>% dplyr::rename("Metabolite" = "x", "Mutualism" = "percent")
```

#Mutual vs. Competed Metabolites

```{r}
shared_metabolites <- full_join(mutual_metabolites, competed_metabolites,)
shared_metabolites[is.na(shared_metabolites)] <- 0
shared_metabolites <- melt(shared_metabolites)
shared_metabolites$value <- as.integer(shared_metabolites$value)

pdf(file='~/Documents/interactions_paper/comp_mutu_metabo.pdf', width=12, height=12)
shared_metabolites %>% 
  mutate(
    value2 = ifelse(variable=="Mutualism", value*(-1),
                        value*1))%>%
    ggplot(aes(x = reorder(Metabolite, value2, FUN = max),y = value2, fill=variable)) + 
    geom_bar(stat = "identity") +
    geom_text(aes(y=value2, label=value), color="black", size=3, hjust = -.3) +
    theme_classic() + ylab("% of All Interactions") + 
    xlab(NULL) +
    scale_y_continuous(labels=c("-100" = "100", "-50" = "50", "0" = "0", "50" = "50", "100" = "100"))+
    scale_fill_manual(values = c("#9DAD9D","#224B5D"))+
    guides(fill=guide_legend(title=NULL))+
    theme(axis.text.x = element_text(size = 10, angle = 45, vjust = 1, hjust = 1), 
          axis.title.x = element_text(size = 20, face = "bold"), axis.text.y = element_text(size = 12),
        legend.text = element_text(size = 15, face = "bold"), legend.position = c(0.8, 0.15))+
    coord_flip()
dev.off()
```
## Find most mutualistic & most competitive bacteria
```{r}
library(dplyr)
library(BSDA)

one_sided_ttest <- function(x, alternative) {
  ttest <- t.test(x, alternative = alternative)
  pvalue <- ttest$p.value
  statistic <- ttest$statistic
  results <- list(pvalue = pvalue, statistic = statistic)
  return(results) # return one-tailed p-value
}

mutualism_ttest <- apply(input_mutualism, 2, one_sided_ttest, alternative = "greater")
mutualism_ttest <- do.call(rbind, lapply(mutualism_ttest, as.data.frame(t)))
GENRE1 <- rownames(mutualism_ttest)
statistic <- unlist(mutualism_ttest$value.statistic)
pvalues <- unlist(mutualism_ttest$value.pvalue)

mutualism_pvalues <- data.frame(GENRE1, pvalues, statistic)
mutualism_pvalues$p.value_adjust<- p.adjust(mutualism_pvalues$pvalues, method = "bonferroni")
mutualism_pvalues_sig <- mutualism_pvalues %>% filter(p.value_adjust <= 0.05) %>% arrange(desc(statistic)) %>% head(5)
mutualism_pvalues_sig <- left_join(mutualism_pvalues_sig, metadata)
View(mutualism_pvalues_sig)
```

```{r}
competitionm_ttest <- apply(input_competition, 2, one_sided_ttest, alternative = "greater")
competitionm_ttest <- do.call(rbind, lapply(competitionm_ttest, as.data.frame(t)))
GENRE1 <- rownames(competitionm_ttest)
statistic <- unlist(competitionm_ttest$value.statistic)
pvalues <- unlist(competitionm_ttest$value.pvalue)

competition_pvalues <- data.frame(GENRE1, pvalues, statistic)
competition_pvalues$p.value_adjust<- p.adjust(competition_pvalues$pvalues, method = "bonferroni")
competition_pvalues_sig <- competition_pvalues %>% filter(p.value_adjust <= 0.05)  %>% arrange(desc(statistic)) %>% head(5)
competition_pvalues_sig <- left_join(competition_pvalues_sig, metadata)
View(competition_pvalues_sig)
```


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
